Query Optimization for Dynamic Imputation

### 2017-07-12 paper/introduction.tex
Add separate results statements

% Implications
Our approach enables an exploratory analysis workflow in which the analyst can issue
standard SQL queries over a data set, even if that data has missing values.
These queries execute between \lowxalphazero{} and \highxalphazero{} times faster than
imputing all missing values and then running queries (the traditional approach). Furthermore, the results obtained with this approach
are similar in quality to those obtained with the traditional imputation approach
--- between \lowsmapealphazero{} and \highsmapealphaone{}
percent --- in our empirical results over real-world data sets (see~\Cref{sec:experiments}
for details).

>>>>

% Implications
Our approach enables an exploratory analysis workflow in which the analyst can issue
standard SQL queries over a data set, even if that data has missing values.
\cameraready{
Using dynamic imputation, these queries execute between \lowxalphazero{} and
\highxalphazero{} times faster than the traditional approach of first imputing all missing
values and then running queries. Empirical results obtained using dynamic imputation
on real-world datasets show errors within \lowsmapealphazero{} to \highsmapealphazero{} percent of
the traditional approach (see~\Cref{sec:experiments} for more details). Alternately,
configuring dynamic imputation to prioritize query runtime yields further speedups of
\lowxalphaone{} to \highxalphaone{} times, with errors of \lowsmapealphaone{} to
\highsmapealphaone{} percent.
}

### 2017-07-12 paper/main.tex
Add separate results statements

\newcommand{\lowxalphazero}{10} % the smallest speed up, comparing a=0 to base table imputation
\newcommand{\highxalphazero}{140} % the largest speed up, comparing a=0 to base table imputation 
\newcommand{\highxalphaone}{1400} % the largest speed up, comparing a=0 OR a=1 to base table imputation

\newcommand{\lowsmapealphazero}{0} % the smallest SMAPE difference, comparing a=0 to base table imputation
\newcommand{\highsmapealphazero}{8} % the largest SMAPE difference, comparing a=0 to base table imputation
\newcommand{\highsmapealphaone}{20} % the largest SMAPE difference, comparing a=1 to base table imputation

\newcommand{\lowcountfractionlostalphazero}{0}
\newcommand{\highcountfractionlostalphazero}{21}
\newcommand{\lowcountfractionlostalphaone}{6}
\newcommand{\highcountfractionlostalphaone}{78}

%\newcommand{\highxalphaone}{16000}
\newcommand{\nullv}{NULL}

>>>>

% Compare to Figure 5
\newcommand{\lowxalphazero}{10} % the smallest speed up, comparing a=0 to base table imputation
\newcommand{\highxalphazero}{140} % the largest speed up, comparing a=0 to base table imputation 
\newcommand{\lowxalphaone}{TODO} % the smallest speed up, comparing a=1 to base table imputation
\newcommand{\highxalphaone}{1400} % the largest speed up, comparing a=1 to base table imputation

% Compare to Table 4
\newcommand{\lowsmapealphazero}{0} % the smallest SMAPE difference, comparing a=0 to base table imputation
\newcommand{\highsmapealphazero}{8} % the largest SMAPE difference, comparing a=0 to base table imputation
\newcommand{\lowsmapealphaone}{0} % the smallest SMAPE difference, comparing a=1 to base table imputation
\newcommand{\highsmapealphaone}{20} % the largest SMAPE difference, comparing a=1 to base table imputation

% Compare to Table 4
\newcommand{\lowcountfractionlostalphazero}{0}
\newcommand{\highcountfractionlostalphazero}{21}
\newcommand{\lowcountfractionlostalphaone}{6}
\newcommand{\highcountfractionlostalphaone}{78}

\newcommand{\nullv}{NULL}
